---
title: "Dissecting host-microbiome interaction effects on phytoplankton microbiome composition and diversity"
author: "Jinny Wu Yang"
date: "2023-12-25"
output: html_document
---

### Set the Global Knitr Options
```{r knitr_global_options, eval = TRUE, echo = TRUE}
# Set the global options
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      warning = FALSE,
                      message= FALSE,
                      fig.path="Figures/",
                      fig.align = "center")
# Set the seed
set.seed(49856)
```


### Load in R-Packages and Set the Working Environment
```{r load libraries and packages}
# Load packages
necessary_packages=c("ggpubr","phyloseq","stats","vegan","ape","dplyr","quantreg","ggplot2","lme4","reshape2")

packages = lapply(necessary_packages, library, character.only = TRUE)

# Set the working Directory
#setwd("~/Feedback-Innate-exp")

### Source written functions in the file Functions.R that is housed within the "Feedback-Innate-exp"
source("Functions_updated_20231031.R")
```

### Import Data 
```{r data import}
RawTable=read.table("Final_table_dada2.tsv",header=T, row.names = 1) ### ASV table
Meta=read.csv("MetaData.csv",header=T, row.names = 1) ###Meta data
RawTaxonomy=read.csv("Taxonomy.csv",header=T, row.names = 1) ###taxonomy data
```

### Data preparation
```{r cleaning ASV table and meta data}
###Removed ASV with 0 reads and community with <2000 reads and matching ASV with taxonomy data and  Metatdata
Table=RawTable[row.names(RawTable) %in% rownames(RawTaxonomy[which(RawTaxonomy$D1!="NA"),]),] ##remove Bacteria-unclassified
Table=filter(Table,rowSums(Table)!=0) ##Remove sum ASV = 0 across all samples
write.csv(colSums(Table),"Table_SampleReads#.csv")
Table=Table[,which(colSums(Table)>=2000)] ##remove community with <2000 reads
rarefied_Table=t(rarefy_even_depth(otu_table(t(Table),taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T))

###Filter Metadata based on the filtered ASV table
Hratio=numeric()
Day=numeric()
Name=numeric()
for (i in 1:ncol(Table)){
  Hratio[i]=filter(Meta,rownames(Meta) == colnames(Table)[i])$Hratio
  Day[i]=filter(Meta,rownames(Meta) == colnames(Table)[i])$Day
  Name[i]=rownames(filter(Meta,rownames(Meta) == colnames(Table)[i]))
}
Filtered_Meta=data.frame(Day,Hratio)
rownames(Filtered_Meta)=Name

### Filter Taxonomy table
RawTaxonomy=read.csv("Taxonomy.csv",header=T, row.names = 1)

Genus=sapply(strsplit(RawTaxonomy[,6],"__", fixed = TRUE), "[", 2)
Family=sapply(strsplit(RawTaxonomy[,5],"__", fixed = TRUE), "[", 2)
Class=sapply(strsplit(RawTaxonomy[,3],"__", fixed = TRUE), "[", 2)
Phylum=sapply(strsplit(RawTaxonomy[,2],"__", fixed = TRUE), "[", 2)
Class[which(is.na(Class))]="Unclassified"
Genus[which(Genus=="Allorhizobium-Neorhizobium-Pararhizobium-Rhizobium")]="A-N-P-R"
Genus[which(Genus=="uncultured anaerobic ammonium-oxidizing bacterium")]="UAAOB"
Genus[which(Genus=="uncultured bacterium")]="Uncultured"
Genus[which(Genus=="uncultured")]="Uncultured"
Genus[which(is.na(Genus))]="Unclassified"
Family[which(Family=="uncultured anaerobic ammonium-oxidizing bacterium")]="UAAOB"
Family[which(is.na(Family))]="Unclassified"
Name_Figure3=paste(Genus,"/",
                 Family,"/",
                 Class)
Name_Figure4=paste(Genus,"\n(",Family,"\n/",Class,")")

Taxonomy=cbind(Phylum,Class,Family,Genus,Name_Figure3,Name_Figure4)
rownames(Taxonomy)=rownames(RawTaxonomy)
##
```


#### Figure 2: Impacts on microbiome composition (Ordination analysis) 
### Calculate distance matrix and PCoA
```{r PCoA}
BC_dist = avgdist(t(Table), 2000,  dmethod = "bray") ## calculate Bray-Curtis distance matrix
BC_dist_matrix=as.matrix(BC_dist, labels=TRUE)
PCOA = pcoa(BC_dist, correction = "cailliez") ## calculate PCoA, correction added in case of negative eigenvalues

###Preparing my table
Day=sapply(strsplit(sapply(strsplit(rownames(PCOA$vectors), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
H=sapply(strsplit(sapply(strsplit(rownames(PCOA$vectors), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
HR=as.numeric(factor(rank(as.numeric(H))))

MyData=data.frame(PCOA$vectors[,1],PCOA$vectors[,2],Day,H)

```

### Plot Figure 2
```{r plot Figure 2}
pdf("Figure 2.pdf", width = 5.5, height = 3.3) 
par(mfrow = c(2,3)) # 2-by-3 grid of plots
par(oma = c(3, 3, 1, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together
COL=c("darkgreen","blue","brown","red","orange","gold","black")
PCH=c(15,0,17,2,16,1,8)
PermanovaTable=list()
OrdinationEachDay(MyData,2,COL,PCH)
#PermanovaTable[[1]]=PERMANOVAandANOSIM(Table,Filtered_Meta,2)

axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3, 0.4), label = rep("", 9), tck = -0.03)
axis(2, las=1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), cex.axis=0.7, line = -0.5, lwd = 0)
text(x=-0.185, y = 0.3, label = "(a) Day 2", cex = 1)

OrdinationEachDay(MyData,4,COL,PCH)

#PermanovaTable[[2]]=PERMANOVAandANOSIM(Table,Filtered_Meta,4)
text(x=-0.185, y = 0.31, label = "(b) Day 4", cex = 1)

OrdinationEachDay(MyData,6,COL,PCH)

#PermanovaTable[[3]]=PERMANOVAandANOSIM(Table,Filtered_Meta,6)
text(x=-0.185, y = 0.31, label = "(c) Day 6", cex = 1)

OrdinationEachDay(MyData,8,COL,PCH)

#PermanovaTable[[4]]=PERMANOVAandANOSIM(Table,Filtered_Meta,8)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1,las=1, cex.axis=0.6,line = -0.7, lwd = 0)
axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3, 0.4), label = rep("", 9), tck = -0.03)
axis(2, las=1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), cex.axis=0.7, line = -0.5, lwd = 0)
text(x=-0.185, y = 0.31, label = "(d) Day 8", cex = 1)

OrdinationEachDay(MyData,10,COL,PCH)

#PermanovaTable[[5]]=PERMANOVAandANOSIM(Table,Filtered_Meta,10)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1,las=1, cex.axis=0.6,line = -0.7, lwd = 0)
text(x=-0.175, y = 0.31, label = "(e) Day 10", cex = 1)

OrdinationEachDay(MyData,12,COL,PCH)

#PermanovaTable[[6]]=PERMANOVAandANOSIM(Table,Filtered_Meta,12)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1, las=1, cex.axis=0.6, line = -0.7, lwd = 0)
text(x=-0.175, y = 0.31, label = "(f) Day 12", cex = 1)

legend(x = c(0.25,0.45), y = c(-0.1,0.34),
       title = "feedback\n-to-innate \nindex",
       legend=c("100%","75%","50%","25%","5%","0%","Original"),
       pch=PCH,
       col=COL,
       cex=0.65, bty="n")

A1=PCOA$values$Rel_corr_eig[1]
A2=PCOA$values$Rel_corr_eig[2]

mtext("Axis PCoA 1 (21.9%)", side = 1, outer = TRUE, line = 1.4, cex=0.7)
mtext("Axis PCoA 2 (14.1%)", side = 2, outer = TRUE, line = 1.7, cex=0.7)
dev.off() 
####
```

##### Bacterial composition of original microbiome and microbiome collected on Day 12
###Calculate ASV respsone to an incresasing Feedback-to-Innate indices: Correlation coefficient
```{r}
##Prepare cor data: ASVreactionCor
##Select Day12 ASV table
Sample=colnames(rarefied_Table)
Day12=rarefied_Table[,which(sapply(strsplit(sapply(strsplit(Sample, "D" , fixed = TRUE), "[", 2), "R" , fixed = TRUE), "[", 1)==12)]
ASVreactionCor=data.frame(matrix(ncol = 3, nrow = nrow(Day12)))
for (i in 1:nrow(Day12)){
  ASV=as.numeric(Day12[i,])
  Hratio=as.numeric(sapply(strsplit(sapply(strsplit(colnames(Day12), "D" , fixed = TRUE), "[", 1), "H" , fixed = TRUE), "[", 2))
  ASVreactionCor[i,1]=cor(ASV,Hratio)
  ASVreactionCor[i,2]=p.adjust(cor.test(ASV,Hratio)$p.value, method = "bonferroni")
  ASVreactionCor[i,3]=sum(ASV)
  rownames(ASVreactionCor)[i]=rownames(Day12[i,])
}
colnames(ASVreactionCor)=c("Cor","adjust.p.value","ReadSum")
```

### Figure 3: Day 0 and Day 12 community compoistion
```{r plot Figure 3}
Sample=colnames(rarefied_Table)
Day12=rarefied_Table[,which(sapply(strsplit(sapply(strsplit(Sample, "D" , fixed = TRUE), "[", 2), "R" , fixed = TRUE), "[", 1)==12)]
Original=rarefied_Table[,which(sapply(strsplit(Sample, "X" , fixed = TRUE), "[", 1)=="CE1")]
Original_Day12_Table=cbind(Original,Day12)
Original_Day12_Table=Original_Day12_Table[rowSums(Original_Day12_Table)>0,]

MergedTable=merge(Original_Day12_Table,Taxonomy[,5],by="row.names")
colnames(MergedTable)[1]="ASV"
colnames(MergedTable)[34]="TAX"

## Label ASV with significant correlated with an increasing Feedback-to-Innate indice
sig_ASV=rownames(ASVreactionCor)[which(ASVreactionCor$adjust.p.value<=0.05 & ASVreactionCor$ReadSum>=600)]
S=numeric()
for (i in 1:length(sig_ASV)){
S[i]=which(MergedTable$ASV==sig_ASV[i])
}
Cor=rep("",nrow(MergedTable))
Cor[S]="sig"

write.csv(MergedTable,"MergedTable.csv")
MergedTable=data.frame(MergedTable,Cor)
Figure3_Data=melt(MergedTable,id=c(1,34,35))
Figure3_Data$variable=sapply(strsplit(as.character(Figure3_Data$variable), "R" , fixed = TRUE), "[", 1)

Figure3_Data$variable = factor(Figure3_Data$variable,levels = c("CE1Xenic","CE1H100D12","CE1H75D12","CE1H50D12","CE1H25D12","CE1H5D12","CE1H0D12"))

## Taking reads means for the sample
Figure3_Data=aggregate(value~ASV+TAX+Cor+variable,Figure3_Data,FUN=mean)


```
###Plot Figure 3
```{r plot Figure 3}

custom_colors = c(
  "#1f78b4", "#dd3497", "#e31a1c", "blue", "gold", "#6a3d9a",
  "#b15928", "#fb8072", "#b2df8a", "#44aa99", "#fdb462", "#80b1d3",
  "#ffed6f", "darkgrey", "bisque", "#bc80bd", "#fccde5", "brown",
  "#8c564b", "#9467bd", "#e377c2", "#332288", "#bcbd22", "#17becf",
  "grey", "#8dd3c7","white", "darkgreen","tan")

NewName=c("Original","100%","75%","50%","25%","5%","0%")

pdf("Figure 3.pdf", width = 12, height = 6) 
ggplot(data=Figure3_Data, aes(x=variable, y=value, fill=TAX, linetype=Cor)) +
  geom_bar(stat="identity",colour = "black", size = 0.2)+
  theme_bw()+
  guides(fill=guide_legend(ncol=3))+
  coord_flip()+
  theme(legend.position="bottom")+
  theme(legend.title=element_blank())+
  theme(legend.text=element_text(size=8))+
  theme(axis.title.x = element_blank(),
        axis.title.y = element_blank())+
  theme(legend.key.size = unit(0.4,'cm'))+
  scale_x_discrete(labels=NewName) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())+
  scale_linetype_manual(values = c("dotted","solid"))+
  geom_bar(color = "black",size=0.4,stat="identity")+
  guides(linetype = "none")+
  scale_fill_manual(values=custom_colors)
dev.off() 
```

##### Figure 4: Identifying bacterial taxa increases/decreases with an incresaeing feedback-to-innate indices
###Matching taxonomy data
```{r match/align taxonomy data}
Tax_Cor=merge(ASVreactionCor,Taxonomy,by="row.names")
Tax_Cor_Over600=Tax_Cor[which(Tax_Cor$ReadSum>=600),] ##>1% of total reads
Tax_Cor_Over600_sig=Tax_Cor_Over600[which(Tax_Cor_Over600$adjust.p.value<=0.05),]
COLOR=numeric()
COLOR[which(Tax_Cor_Over600_sig$Cor>=0)]="darkgreen"
COLOR[which(Tax_Cor_Over600_sig$Cor<=0)]="orange"
Figure4_Data=data.frame(Tax_Cor_Over600_sig,COLOR)
Figure4_Data$Name_Figure4 = with(Figure4_Data, reorder(Name_Figure4, Cor, mean)) 

```

###Plot Figure 4
```{r plot Figure 4}
###Plot Cor
pdf("Figure 4.pdf", width = 8, height = 5) 
ggplot(data=Figure4_Data,aes(y=Name_Figure4, x=Cor,horizontal=TRUE))+
  theme_bw() + 
  geom_point(fill=COLOR, 
             size = 5.5, color='black',shape=21) +
  theme(axis.text=element_text(size=7),
        axis.title = element_text(size = 8),
        plot.margin = margin(0.05,0.05,0.001,0.05, "cm")) +
  xlab("Pearson's Correlation coefficient") +
  ylab("") + 
  theme(axis.title.y=element_text(angle=0))+ 
  theme(axis.text.y = element_text(angle = 0, hjust = 1, colour = "black",
                                   face = "italic"))
dev.off() 
```

###Figure 5: Diversity change with an incresaeing feedback-to-innate index (on Day 12)
```{r plot Prepare Diversity table}
Table=rarefied_Table
Richness=colSums(ifelse(Table> 1,1,0))
Shannon=diversity(t(Table),"shannon")
Simpson=diversity(t(Table),"simpson")
invSimpson=diversity(t(Table),"invsimpson")
Evenness=invSimpson/Richness
Day=sapply(strsplit(sapply(strsplit(names(Richness), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
H=sapply(strsplit(sapply(strsplit(names(Richness), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
Figure5_Data=data.frame(Richness,Shannon,Simpson,Evenness,Day,H)
Figure5_Data=Figure5_Data[order(as.numeric(Figure5_Data$H)),]
Figure5_Data=Figure5_Data
Figure5_Data$H=as.numeric(Figure5_Data$H)
```

###Plot Figure 5: Day 12 only
```{r Figure 5}
pdf("Figure 5.pdf", width = 6, height =2.2) 
#D=1, Richness
#D=2, Shannon
#D=3, Simpson
#D=4, Evenness
par(mfrow = c(1,3)) # 3-by-2 grid of plots
par(oma = c(1, 1, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(3, 3, 0, 0)) # make the plots be closer together

Figure5_Data_Day12=filter(Figure5_Data, Figure5_Data$Day==12)
  
figure5(Figure5_Data_Day12,1,15,31)
mtext("(a)",at=1,line=-1,cex=0.7)
figure5(Figure5_Data_Day12,4,0.1,0.4)
mtext("(b)",at=1,line=-1,cex=0.7)
figure5(Figure5_Data_Day12,2,1.5,2.5)
mtext("(c)",at=1,line=-1,cex=0.7)

mtext("Feedback-to-innate index", side = 1, outer = TRUE, line = -1.5, cex=0.9)
mtext("Diversity indices", side = 2, outer = TRUE, line = -0.5, at=0.6,cex=0.9)
mtext("Richness", side = 3, outer = TRUE, line = 0, cex=0.9, at=0.2, font=1)
mtext("Evenness", side = 3, outer = TRUE, line = 0, cex=0.9, at=0.55,font=1)
mtext("Shannon", side = 3, outer = TRUE, line = 0, cex=0.9, at=0.88, font=1)
dev.off() 
```


##### Sumpplemenotry figures 
###Figure S1: Rarefaction
```{r Figure S1}

```

###Figure S3: Linear regression assumptions test.
```{r Figure S3}
############ testing linear regression assumption######
###Evenness
l=lm(Figure5_Data_Day12[,4]~as.numeric(Figure5_Data_Day12$H))
### Residual vs Fitted
plot(residuals(l),fitted(l),xlab = "Residuals",ylab = "Fitted")
MEAN=mean(residuals(l))
  
  State = vector('expression',4)
  State[1] = substitute(expression(italic(Residuals:Mean) == MYVALUE), 
                        list(MYVALUE = format(MEAN, digits = 2)))[2]
  State[2] = substitute(expression(italic(D-W:Autocorrelation) == MYVALUE), 
                        list(MYVALUE = format(as.numeric(durbinWatsonTest(l)[1]), digits = 2)))[2]
  State[3] = substitute(expression(italic(D-W:Statistic) == MYVALUE), 
                        list(MYVALUE = format(as.numeric(durbinWatsonTest(l)[2]), digits = 2)))[2]
  State[4] = substitute(expression(italic(D-W:p-value) == MYVALUE), 
                        list(MYVALUE = format(durbinWatsonTest(l)[3], digits = 2)))[2]
  #legend("bottomleft",legend=State,  text.col=c("blue"), bty = 'n',cex=0.6)
  legend("bottomleft",legend=State,  text.col=c("black"), bty = 'n',cex=0.6)
  
### assumption of independence:Durbin Watson test
library(car)
durbinWatsonTest(l) 

```

###Figure S4: Diveristy plot 
```{r Figure S4}
pdf("Figure S4.pdf", width = 6, height = 3.5) 
#D=1, Richness
#D=2, Shannon
#D=3, Simpson
#D=4, Evenness
par(mfrow = c(3,6)) # 3-by-6 grid of plots
par(oma = c(4, 4, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together
Label=c("(a)","(b)","(c)","(d)","(e)","(f)")
Xaxis=F
Ordered_MyData=MyData[order(as.numeric(MyData$H)),]
MyData=Ordered_MyData
MyData$H=as.numeric(MyData$H)
MyData$Day=as.numeric(MyData$Day)

SplitBy_Day=split(MyData, MyData$Day)
##Plot Richness
a=5
b=41
c=5
Xaxis=FALSE
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Richness
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Richness
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}
#plot Evenness
a=0.07
b=0.5
c=0.1
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Evenness
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Evenness
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}
#plot Shannon
a=0.9
b=2.8
c=0.5
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Shannon
Xaxis=TRUE
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Shannon
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}

mtext("Feedback-to-Innate index", side = 1, outer = TRUE, line = 1.5, cex=0.8)
mtext("Richness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Evenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Shannon index", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.2, font=1)
DayLab=c("Day2","Day 4","Day 6","Day 8","Day 10","Day 12")
mtext(DayLab, side = 3, outer = TRUE, line = 0, cex=0.8, 
      at=c(0.075,0.25,0.425,0.575,0.75,0.925), font=1)

dev.off() 

```




###Figure S5: Additional experiment
```{r Figure S3}
library(ggpubr)
library(phyloseq)
library(stats)
library(dplyr)
Table=read.table("AE_Final_table_dada2.tsv",header=T, row.names = 1)
Meta=read.csv("AE_MetaData.csv",header=T, row.names = 1)
Sample_all=colnames(Table)
ps.rarefied = rarefy_even_depth(otu_table(Table,taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T)

###############Ordination analysis##############
Table_rarefied=data.frame(t(ps.rarefied))
Sample_all=colnames(Table_rarefied)
library(vegan)
library(ape)
library(dplyr)
# First step is to calculate a distance matrix. 
# Here we use Bray-Curtis distance metric
BC_dist = avgdist(t(Table),1200,  dmethod = "bray")

# PCoA is not included in vegan. 
# We will use the ape package instead
library(ape)
# Some distance measures may result in negative eigenvalues. In that case, add a correction:
PCOA = pcoa(BC_dist, correction = "cailliez")

###Preparing my table
rownames(PCOA$vectors)==rownames(Meta)
Day=Meta$Day
Ratio=Meta$Hratio
Treatment=Meta$Treatment

MyData=data.frame(PCOA$vectors[,1],PCOA$vectors[,2],Day,Treatment,Ratio)

pdf("Figure S3.pdf", width = 6, height = 3.5) 

par(mfrow = c(2,3)) # 2-by-2 grid of plots
par(oma = c(3, 3, 1, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0), xpd=TRUE) # make the plots be closer together

DAY=c(2,4,6,8,10)
DAY_Name=c("Day 2","Day 4","Day 6","Day 8","Day 10")
Xaxis=c(F,F,T,T,T,T)
Yaxis=c(T,F,F,T,F,F)
for (i in 1:5){
  day=DAY[i]
  DDay=filter(MyData, MyData$Day==day)
  plot(DDay[,1],DDay[,2],pch=1, col="white", 
       xlim=c(min(MyData[,1]),max(MyData[,1])),
       ylim=c(min(MyData[,2]),max(MyData[,2])),
       type="b",xaxt="n",yaxt="n", 
       xlab="", ylab="")
  DD=filter(DDay, DDay$Treatment=="A")
  points(DD[,1],DD[,2],pch=1, col="black")
  
  DD=filter(DDay, DDay$Treatment=="D")
  points(DD[,1],DD[,2],pch=2, col="black")
  
  DD=filter(DDay, DDay$Treatment=="C")
  DD50=filter(DD, DD$Ratio==50)
  DD95=filter(DD, DD$Ratio==95)
  points(DD50[,1],DD50[,2],pch=17, col="grey")
  points(DD95[,1],DD95[,2],pch=17, col="black")
  
  DD=filter(DDay, DDay$Treatment=="H")
  DD50=filter(DD, DD$Ratio==50)
  DD95=filter(DD, DD$Ratio==95)
  points(DD50[,1],DD50[,2],pch=15, col="grey")
  points(DD95[,1],DD95[,2],pch=15, col="black")
  text(x=-0.325, y = 0.25, label = DAY_Name[i], cex = 1)
  DDay=filter(MyData, MyData$Day==0)
  points(DDay[,1],DDay[,2],pch=8, col="black")
  if (Xaxis[i]==T){
    axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
    axis(1, las=1, cex.axis=0.6, line = -0.55, lwd = 0)    
  }
  if (Yaxis[i]==T){
    axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
    axis(2, las=1, cex.axis=0.6, line = -0.55, lwd = 0)    
  }
}

LEGEND=c("95%-to-5% Feedback-to-DOM","50%-to-50% Feedback-to-DOM",
         "95%-to-5% Media-to-DOM","50%-to-50% Media-to-DOM",
         "100% innate DOM","Chlorella sorokoniana",
         "Original microbiome at Day0")

legend("topleft", inset=c(1.05, 0.05),
       title = "",
       legend=LEGEND,
       pch=c(15,15,17,17,2,1,8),
       col=c("black","grey",
             "black","gray",
             "black","black","black"),
       cex=0.9, bty="n", xpd=NA)

mtext("PCoA axis 1 (38.4 %)", side = 1, outer = TRUE, line = 1.4, cex=0.8)
mtext("PCoA axis 1 (13.8 %)", side = 2, outer = TRUE, line = 1.4, cex=0.8)
dev.off() 
```


###Figure S6 and S7: Richness and eveness in function of select phyla 
```{r Figure S5 and S6}

Table_oldold=read.table("Final_table_dada2.tsv",header=T, row.names = 1)
Meta=read.csv("MetaData.csv",header=T, row.names = 1)
Taxonomy=read.csv("metadata_taxonomy_HandMade.csv",header=T, row.names = 1)

###remove Bacteria-unclassified####
Table_Alpha=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Alphaproteobacteria"),]),]
Table_Bact=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Bacteroidia"),]),]
Table_Gamma=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Gammaproteobacteria"),]),]
GammaTax=which(Taxonomy$D2=="D_2__Gammaproteobacteria")

Table_Actino=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Actinobacteria"),]),]


FigureS4_Diveristy=function(Table_old){
  #########Rarefaction######
  ps.rarefied = rarefy_even_depth(otu_table(t(Table_old),taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T)
  
  Table_rarefied=t(ps.rarefied)
  Sample_all=colnames(Table_rarefied)
  Table=Table_rarefied[,which(sapply(strsplit(Sample_all, "H" , fixed = TRUE), "[", 1)=="CE1")]
  ##########################
  
  Richness=colSums(ifelse(Table> 1,1,0))
  Shannon=diversity(t(Table),"shannon")
  Simpson=diversity(t(Table),"simpson")
  invSimpson=diversity(t(Table),"invsimpson")
  Evenness=invSimpson/Richness
  Day=sapply(strsplit(sapply(strsplit(names(Richness), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
  H=sapply(strsplit(sapply(strsplit(names(Richness), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
  MyData=data.frame(Richness,Shannon,Simpson,Evenness,Day,H)
  return(MyData)
  ##########################
}
Alpha=FigureS4_Diveristy(Table_Alpha)
Gamma=FigureS4_Diveristy(Table_Gamma)
Bact=FigureS4_Diveristy(Table_Bact)
#Beta=FigureS4_Diveristy(Table_Beta)

Diveristy_Day8_10_12=function(MyData){
  Ordered_MyData=MyData[order(as.numeric(MyData$H)),]
  MyData=Ordered_MyData
  MyData$H=as.numeric(MyData$H)
  
  DDay8=filter(MyData, MyData$Day==8)
  DDay10=filter(MyData, MyData$Day==10)
  DDay12=filter(MyData, MyData$Day==12)
  LIST=list(DDay8,DDay10,DDay12)
  return(LIST)
}

Alpha_list=Diveristy_Day8_10_12(Alpha)
Gamma_list=Diveristy_Day8_10_12(Gamma)
Bact_list=Diveristy_Day8_10_12(Bact)

#####Diversity plot###
source("Functions_20220504.R")
par(mfrow = c(3,2)) # 3-by-6 grid of plots
par(oma = c(4, 5.5, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together


Each_plot=function(DDay10,D,Xaxis,Yaxis,a,b,c){
  
  plot(as.numeric(DDay10$H),DDay10[,D], xaxt="n", yaxt="n",
       ylim=c(a,b),
       xlim=c(-5,105))
  
  # fit the 2rd quadrilles regressions
  y=DDay10[,D]
  x=DDay10$H
  fit2 <- lm(y~poly(x,2,raw=TRUE))
  xx <- seq(0,100, length=50)
  summary(fit2)
  p2=summary(fit2)$coefficient[3,4]
  if (p2<=0.05){L2=1}else{L2=2}
  if (p2<=0.001){p2="<0.001"}else{p2=p2}
  lines(xx, predict(fit2, data.frame(x=xx)), col="blue",lty=L2)
  
  # fit the linear regression
  l=lm(DDay10[,D]~as.numeric(DDay10$H))
  p=summary(l)$coefficient[2,4]
  if (p<=0.05){L=1}else{L=2}
  if (p<=0.001){p="<0.001"}else{p=p}
  abline(l,lty=L)
  State = vector('expression',2)
  State[1] = substitute(expression(italic(p1:p-value) == MYVALUE), 
                        list(MYVALUE = format(p, digits = 2)))[2]
  State[2] = substitute(expression(italic(p2:p-value) == MYVALUE), 
                        list(MYVALUE = format(p2, digits = 2)))[2]
  
  legend("topright",legend=State, bty = 'n',cex=0.8,text.col=c("black","blue"))
  #text(-4.5,b*0.99, label = Label1, cex=0.9)
  
  if (Xaxis==TRUE) {
    axis(1, at = c(0,25,50,75,100), 
         label = rep("", 5), 
         tck = -0.04)
    axis(1, at = c(0,25,50,75,100), 
         label = c("0%","25%","50%","75%","100%"), 
         cex.axis=0.6,line = -0.7, lwd = 0)
    axis(1, at = 5, 
         label = "", 
         tck = -0.03)
    axis(1, at = 5, 
         label = "5%", 
         cex.axis=0.6,line = -1.1, lwd = 0)
  }
  
  if (Yaxis==TRUE) {
    axis(2, tck = -0.04, at = seq(a,b, by = c), 
         label = rep("", length(seq(a,b, by = c))))
    axis(2, las=1, cex.axis=0.7, at = seq(a,b, by = c),
         line = -0.4, lwd = 0)
  }
  
  
}  

Each_plot(Alpha_list[[2]],1,FALSE,TRUE,1,15,2)
Each_plot(Alpha_list[[3]],1,FALSE,FALSE,1,15,2)

Each_plot(Gamma_list[[2]],1,FALSE,TRUE,1,15,2)
Each_plot(Gamma_list[[3]],1,FALSE,FALSE,1,15,2)


Each_plot(Bact_list[[2]],1,TRUE,TRUE,1,15,2)
Each_plot(Bact_list[[3]],1,TRUE,FALSE,1,15,2)


mtext("Feedback-to-innate index", side = 1, outer = TRUE, line = 2, cex=0.8)
mtext("Alphaproteobacteria\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Gammaproteobacteria\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Bacteroidia\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.15,font=1)
mtext("Day 10", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.25, font=1)
mtext("Day 12", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.75, font=1)

######Evenness #######
#####Diversity plot###
source("Functions_20220504.R")
par(mfrow = c(3,2)) # 3-by-6 grid of plots
par(oma = c(4, 5.5, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together

Each_plot(Alpha_list[[2]],4,FALSE,TRUE,0,0.7,0.2)
Each_plot(Alpha_list[[3]],4,FALSE,FALSE,0,0.7,0.2)

Each_plot(Gamma_list[[2]],4,FALSE,TRUE,0,0.7,0.2)
Each_plot(Gamma_list[[3]],4,FALSE,FALSE,0,0.7,0.2)

Each_plot(Bact_list[[2]],4,TRUE,TRUE,0,0.7,0.2)
Each_plot(Bact_list[[3]],4,TRUE,FALSE,0,0.7,0.2)

mtext("Feedback-to-innate index", side = 1, outer = TRUE, line = 2, cex=0.8)
mtext("Alphaproteobacteria\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Gammaproteobacteria\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Bacteroidia\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.15,font=1)
mtext("Day 10", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.25, font=1)
mtext("Day 12", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.75, font=1)
```

###Figure S8: Microbiome detachment experiment
```{r Figure S8}
pdf("Figure S8.pdf", width = 8, height = 5) 
#No treatment
aP1_A=46
aP2_A=134
aP3_A=139
MeanContol_T1=mean(c(aP1_A,aP2_A,aP3_A))

#rep x5
W30s1_A=91
W30s2_A=57
W30s3_A=65
T30s_x5_r1=(W30s1_A-MeanContol_T1)/MeanContol_T1
T30s_x5_r2=(W30s2_A-MeanContol_T1)/MeanContol_T1
T30s_x5_r3=(W30s3_A-MeanContol_T1)/MeanContol_T1

#rep x10
W60s1_A=69
W60s2_A=41
W60s3_A=94
T60s_x10_r1=(W60s1_A-MeanContol_T1)/MeanContol_T1
T60s_x10_r2=(W60s2_A-MeanContol_T1)/MeanContol_T1
T60s_x10_r3=(W60s3_A-MeanContol_T1)/MeanContol_T1

#rep x15
W6r1_A=40
W6r2_A=46
W6r3_A=60
T60s_x15_r1=(W6r1_A-MeanContol_T1)/MeanContol_T1
T60s_x15_r2=(W6r2_A-MeanContol_T1)/MeanContol_T1
T60s_x15_r3=(W6r3_A-MeanContol_T1)/MeanContol_T1

#######
#No treatment
bP1_A=225
bP2_A=207
bP3_A=232
bP4_A=307
MeanContol_T2=mean(c(bP1_A,bP2_A,bP3_A,bP4_A))

#rep 60sx1
W30s1_A=299
W30s2_A=257
W30s3_A=476
W30s4_A=543
W30s5_A=266
W30s6_A=160
aT60s_x1_r1=(W30s1_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r2=(W30s2_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r3=(W30s3_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r4=(W30s4_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r5=(W30s5_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r6=(W30s6_A-MeanContol_T2)/MeanContol_T2

#rep 60sx3
W60s1_A=636
W60s2_A=323
W60s3_A=337
W60s4_A=453
W60s5_A=173
W60s6_A=230
T60s_x3_r1=(W60s1_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r2=(W60s2_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r3=(W60s3_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r4=(W60s4_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r5=(W60s5_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r6=(W60s6_A-MeanContol_T2)/MeanContol_T2

#rep 60sx6
W6r1_A=246
W6r2_A=269
W6r3_A=345
W6r4_A=376
W6r5_A=278
W6r6_A=181

T60s_x6_r1=(W6r1_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r2=(W6r2_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r3=(W6r3_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r4=(W6r4_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r5=(W6r5_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r6=(W6r6_A-MeanContol_T2)/MeanContol_T2
#########

#No treatment
cP1_A=43
cP2_A=45
cP3_A=35
cP4_A=43
cP5_A=41
cP6_A=57
MeanContol_T3=mean(c(cP1_A,cP2_A,cP3_A,cP4_A,cP5_A,cP6_A))

#30sx1
W30s1_A=50
W30s2_A=53
W30s3_A=51
W30s4_A=51
W30s5_A=69
W30s6_A=56
T30s_x1_r1=(W30s1_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r2=(W30s2_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r3=(W30s3_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r4=(W30s4_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r5=(W30s5_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r6=(W30s6_A-MeanContol_T3)/MeanContol_T3


#30sx2
W60s1_A=59
W60s2_A=73
W60s3_A=81
W60s4_A=71
W60s5_A=66
W60s6_A=63
T30s_x2_r1=(W60s1_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r2=(W60s2_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r3=(W60s3_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r4=(W60s4_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r5=(W60s5_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r6=(W60s6_A-MeanContol_T3)/MeanContol_T3


# 60sx1
W6r1_A=66
W6r2_A=58
W6r3_A=60
W6r4_A=69
W6r5_A=66
W6r6_A=68
bT60s_x1_r1=(W6r1_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r2=(W6r2_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r3=(W6r3_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r4=(W6r4_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r5=(W6r5_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r6=(W6r6_A-MeanContol_T3)/MeanContol_T3

T30sx1=c(T30s_x1_r1,T30s_x1_r2,T30s_x1_r3,T30s_x1_r4,T30s_x1_r5,T30s_x1_r6)*100
T30sx2=c(T30s_x2_r1,T30s_x1_r2,T30s_x2_r3,T30s_x2_r4,T30s_x2_r5,T30s_x2_r6)*100
T30sx5=c(T30s_x5_r1,T30s_x5_r2,T30s_x5_r3)*100
T60sx1=c(bT60s_x1_r1,bT60s_x1_r2,bT60s_x1_r3,bT60s_x1_r4,bT60s_x1_r5,bT60s_x1_r6)*100
T60sx3=c(T60s_x3_r1,T60s_x3_r2,T60s_x3_r3,T60s_x3_r4,T60s_x3_r5,T60s_x3_r6)*100
T60sx6=c(T60s_x6_r1,T60s_x6_r2,T60s_x6_r3,T60s_x6_r4,T60s_x6_r5,T60s_x6_r6)*100
T60sx10=c(T60s_x10_r1,T60s_x10_r2,T60s_x10_r3)*100
T60sx15=c(T60s_x15_r1,T60s_x15_r2,T60s_x15_r3)*100

All=data.frame(T30sx1,T30sx2,T60sx1,T30sx5,T60sx3,T60sx6,T60sx10,T60sx15)

par(mar = c(5, 5, 2, 2)) # make the plots be closer together
par(mgp=c(3,1.25,0))
boxplot(All,ylab="% of living bacteria extracted with sonication",
        xlab="Sonication treatments",
        names=c("30 seconds\nx1 time","30 seconds\nx2 times","60 seconds\nx1 times",
                 "30 seconds\nx5 time","60 seconds\nx3 times","60 seconds\nx6 times",
                 "60 seconds\nx10 times","60 seconds\nx15 times"), col="white",cex.axis=0.765)
  stripchart(All, vertical = TRUE, 
           add = TRUE, pch = 1, col = 'black',cex=1.5)
abline(h=0,lty=2,col="grey")
text(2,95,paste("Mean =", format(mean(T30sx2), digits = 3)),cex=0.8)
text(3,66,paste("Mean =", format(mean(T60sx1), digits = 3)),cex=0.8)
dev.off() 
```