---
title: "Dissecting host-microbiome interaction effects on phytoplankton microbiome composition and diversity"
author: "Jinny Wu Yang"
date: "2023-03-09"
output: html_document
---

### Set the Global Knitr Options
```{r knitr_global_options, eval = TRUE, echo = TRUE}
# Set the global options
knitr::opts_chunk$set(eval = TRUE, 
                      echo = TRUE, 
                      warning = FALSE,
                      message= FALSE,
                      fig.path="Figures/",
                      fig.align = "center")
# Set the seed
set.seed(49856)
```


### Load in R-Packages and Set the Working Environment
```{r load libraries and packages}
# Load packages
necessary_packages=c("ggpubr","phyloseq","stats","vegan","ape","dplyr","quantreg","ggplot2","lme4")
packages = lapply(necessary_packages, library, character.only = TRUE)

# Set the working Directory
setwd("~/Feedback-Innate-exp")

### Source written functions in the file Functions.R that is housed within the "Feedback-Innate-exp"
source("Functions.R")
```

### Import Data 
```{r data import}
RawTable=read.table("Final_table_dada2.tsv",header=T, row.names = 1) ### ASV table
Meta=read.csv("MetaData.csv",header=T, row.names = 1) ###Meta data
Taxonomy=read.csv("Taxonomy.csv",header=T, row.names = 1) ###taxonomy data
```


### Removed 0 ASV and community with <2000 reads and matching ASV with taxonomy data and  Metatdata
```{r cleaning ASV table}
Table=RawTable[row.names(RawTable) %in% rownames(Taxonomy[which(Taxonomy$D1!="NA"),]),] ##remove Bacteria-unclassified
Table=filter(Table,rowSums(Table)!=0) ##Remove ASV is zero in all samples
write.csv(colSums(Table),"Table_SampleReads#.csv")
Table=Table[,which(colSums(Table)>=2000)] ##remove community with <2000 reads

###Filter Metadata based on the filtered ASV table
Hratio=numeric()
Day=numeric()
Name=numeric()
for (i in 1:ncol(Table)){
  Hratio[i]=filter(Meta,rownames(Meta) == colnames(Table)[i])$Hratio
  Day[i]=filter(Meta,rownames(Meta) == colnames(Table)[i])$Day
  Name[i]=rownames(filter(Meta,rownames(Meta) == colnames(Table)[i]))
}
Filtered_Meta=data.frame(Day,Hratio)
rownames(Filtered_Meta)=Name

##
```


## Impacts on microbiome composition (Ordination analysis) 
### Calculate distance matrix and PCoA
```{r PCoA}
BC_dist = avgdist(t(Table), 2000,  dmethod = "bray") ## calculate Bray-Curtis distance matrix
BC_dist_matrix=as.matrix(BC_dist, labels=TRUE)
PCOA = pcoa(BC_dist, correction = "cailliez") ## calculate PCoA, correction added in case of negative eigenvalues

###Preparing my table
Day=sapply(strsplit(sapply(strsplit(rownames(PCOA$vectors), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
H=sapply(strsplit(sapply(strsplit(rownames(PCOA$vectors), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
HR=as.numeric(factor(rank(as.numeric(H))))

MyData=data.frame(PCOA$vectors[,1],PCOA$vectors[,2],Day,H)

```

### Figure 2 plotting
```{r plot Figure 2}
par(mfrow = c(2,3)) # 2-by-3 grid of plots
par(oma = c(3, 3, 1, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together

PermanovaTable=list()
OrdinationEachDay(MyData,2)
PermanovaTable[[1]]=PERMANOVAandANOSIM(Table,Filtered_Meta,2)

axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3, 0.4), label = rep("", 9), tck = -0.03)
axis(2, las=1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), cex.axis=0.7, line = -0.5, lwd = 0)
text(x=-0.2, y = 0.3, label = "(a) Day 2", cex = 1)

OrdinationEachDay(MyData,4)

PermanovaTable[[2]]=PERMANOVAandANOSIM(Table,Filtered_Meta,4)
text(x=-0.2, y = 0.31, label = "(b) Day 4", cex = 1)

OrdinationEachDay(MyData,6)

PermanovaTable[[3]]=PERMANOVAandANOSIM(Table,Filtered_Meta,6)
text(x=-0.2, y = 0.31, label = "(c) Day 6", cex = 1)

OrdinationEachDay(MyData,8)

PermanovaTable[[4]]=PERMANOVAandANOSIM(Table,Filtered_Meta,8)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1,las=1, cex.axis=0.6,line = -0.7, lwd = 0)
axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3, 0.4), label = rep("", 9), tck = -0.03)
axis(2, las=1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), cex.axis=0.7, line = -0.5, lwd = 0)
text(x=-0.2, y = 0.31, label = "(d) Day 8", cex = 1)

OrdinationEachDay(MyData,10)

PermanovaTable[[5]]=PERMANOVAandANOSIM(Table,Filtered_Meta,10)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1,las=1, cex.axis=0.6,line = -0.7, lwd = 0)
text(x=-0.2, y = 0.31, label = "(e) Day 10", cex = 1)

OrdinationEachDay(MyData,12)

PermanovaTable[[6]]=PERMANOVAandANOSIM(Table,Filtered_Meta,12)
axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
axis(1, las=1, cex.axis=0.6, line = -0.7, lwd = 0)
text(x=-0.2, y = 0.31, label = "(f) Day 12", cex = 1)

legend(x = c(0.28,0.45), y = c(-0.1,0.34),
       title = "feedback\n-to-innate \nindex",
       legend=c("100%","75%","50%","25%","5%","0%","Original"),
       pch=c(17,16,17,15,2,1,8),
       col=c("black","black","gray","gray","black","black","black"),
       cex=0.65, bty="n")

A1=PCOA$values$Rel_corr_eig[1]
A2=PCOA$values$Rel_corr_eig[2]

mtext("Axis PCoA 1 (21.9%)", side = 1, outer = TRUE, line = 1.4, cex=0.8)
mtext("Axis PCoA 2 (14.1%)", side = 2, outer = TRUE, line = 1.4, cex=0.8)

####
```


### Table S1 Premanova analysis 
```{r Table S1}
PERMANOVA=matrix(0,6,5)
for (i in 1:6){
  PERMANOVA[i,]=as.numeric(PermanovaTable[[i]][1,])
}
colnames(PERMANOVA)=colnames(PermanovaTable[[i]][1,])
rownames(PERMANOVA)=c("Day 2", "Day 4", "Day 6", "Day 8","Day 10","Day 12")
write.csv(PERMANOVA,"PERMANOVA.csv")
```


## Impacts on Microbiome diversty
### Calcualting diveristy indices (richness, evenness and Shannon)
```{r diversity indices}
ps.rarefied = rarefy_even_depth(otu_table(t(Table),taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T)
Table_rarefied=t(ps.rarefied)
Sample_all=colnames(Table_rarefied)
Table=Table_rarefied[,which(sapply(strsplit(Sample_all, "H" , fixed = TRUE), "[", 1)=="CE1")]

Richness=colSums(ifelse(Table> 1,1,0))
Shannon=diversity(t(Table),"shannon")
Simpson=diversity(t(Table),"simpson")
invSimpson=diversity(t(Table),"invsimpson")
Evenness=invSimpson/Richness
Day=sapply(strsplit(sapply(strsplit(names(Richness), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
H=sapply(strsplit(sapply(strsplit(names(Richness), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
MyData=data.frame(Richness,Shannon,Simpson,Evenness,Day,H)
```
### Figure 3
```{r plot Figure 3}
#D=1, Richness
#D=2, Shannon
#D=3, Simpson
#D=4, Evenness
par(mfrow = c(3,2)) # 3-by-2 grid of plots
par(oma = c(4, 4, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together
Label=c("(a)","(b)","(c)","(d)","(e)","(f)")
a=15
b=31
c=2
Xaxis=F
Label[1]
Label[2]
Ordered_MyData=MyData[order(as.numeric(MyData$H)),]
MyData=Ordered_MyData
MyData$H=as.numeric(MyData$H)
Figure3=function(MyData,D,a,b,c,Xaxis,Label1,Label2){
  DDay10=filter(MyData, MyData$Day==10)
  DDay12=filter(MyData, MyData$Day==12)
  
  plot(as.numeric(DDay10$H),DDay10[,D], xaxt="n", yaxt="n",
       ylim=c(a,b),
       xlim=c(-5,105))
  axis(2, tck = -0.04, at = seq(a,b, by = c), 
       label = rep("", length(seq(a,b, by = c))))
  axis(2, las=1, cex.axis=0.7, at = seq(a,b, by = c),
       line = -0.4, lwd = 0)
  
  # fit the 2rd quadrilles regressions
  y=DDay10[,D]
  x=DDay10$H
  fit2 <- lm(y~poly(x,2,raw=TRUE))
  xx <- seq(0,100, length=50)
  summary(fit2)
  p2=summary(fit2)$coefficient[3,4]
  if (p2<=0.05){L2=1}else{L2=2}
  if (p2<=0.001){p2="<0.001"}else{p2=p2}
  lines(xx, predict(fit2, data.frame(x=xx)), col="blue",lty=L2)
  
  # fit the linear regression
  l=lm(DDay10[,D]~as.numeric(DDay10$H))
  p=summary(l)$coefficient[2,4]
  if (p<=0.05){L=1}else{L=2}
  if (p<=0.001){p="<0.001"}else{p=p}
  abline(l,lty=L)
  State = vector('expression',2)
  State[1] = substitute(expression(italic(p1:p-value) == MYVALUE), 
                         list(MYVALUE = format(p, digits = 2)))[2]
  State[2] = substitute(expression(italic(p2:p-value) == MYVALUE), 
                        list(MYVALUE = format(p2, digits = 2)))[2]

  legend("topright",legend=State, bty = 'n',cex=0.8,text.col=c("black","blue"))
  text(-4.5,b*0.99, label = Label1, cex=0.9)
  if (Xaxis==TRUE) {
    axis(1, at = c(0,25,50,75,100), 
         label = rep("", 5), 
         tck = -0.04)
    axis(1, at = c(0,25,50,75,100), 
         label = c("0%","25%","50%","75%","100%"), 
         cex.axis=0.6,line = -0.7, lwd = 0)
    axis(1, at = 5, 
         label = "", 
         tck = -0.03)
    axis(1, at = 5, 
         label = "5%", 
         cex.axis=0.6,line = -1.1, lwd = 0)
  }
    
  plot(as.numeric(DDay12$H),DDay12[,D], xaxt="n", yaxt="n"
       ,ylim=c(a,b),
       xlim=c(-5,105))
  l=lm(DDay12[,D]~as.numeric(DDay12$H))
  
  # fit the 2rd quadrilles regressions
  y=DDay12[,D]
  x=DDay12$H
  fit2 <- lm(y~poly(x,2,raw=TRUE))
  
  xx <- seq(0,100, length=50)
  summary(fit2)
  p2=summary(fit2)$coefficient[3,4]
  if (p2<=0.05){L2=1}else{L2=2}
  if (p2<=0.001){p2="<0.001"}else{p2=p2}
  lines(xx, predict(fit2, data.frame(x=xx)), col="blue",lty=L2)
  
  #fit linear regression
  fit1 <- lm(y~poly(x,1,raw=TRUE))
  p=summary(fit1)$coefficient[2,4]
  if (p<=0.05){L=1}else{L=2}
  if (p<=0.001){p="<0.001"}else{p=p}
  lines(xx, predict(fit1, data.frame(x=xx)), col="black",lty=L)

  State = vector('expression',2)
  State[1] = substitute(expression(italic(p1:p-value) == MYVALUE), 
                        list(MYVALUE = format(p, digits = 2)))[2]
  State[2] = substitute(expression(italic(p2:p-value) == MYVALUE), 
                        list(MYVALUE = format(p2, digits = 2)))[2]

  legend("topright",legend=State,  text.col=c("black","blue"), bty = 'n',cex=0.8)
  text(-4.5,b*0.99, label = Label2, cex=0.9)
  
  if (Xaxis==TRUE) {
    axis(1, at = c(0,25,50,75,100), 
         label = rep("", 5), 
         tck = -0.04)
    axis(1, at = c(0,25,50,75,100), 
         label = c("0%","25%","50%","75%","100%"), 
         cex.axis=0.6,line = -0.7, lwd = 0)
    axis(1, at = 5, 
         label = "", 
         tck = -0.03)
    axis(1, at = 5, 
         label = "5%", 
         cex.axis=0.6,line = -1.1, lwd = 0)
  }
  
  }  
Figure3(MyData,1,15,31,2,FALSE,Label[1],Label[2])
Figure3(MyData,4,0.14,0.36,0.03,FALSE,Label[3],Label[4])
Figure3(MyData,2,1.6,2.6,0.2,TRUE,Label[5],Label[6])

mtext("Feedback-to-Innate index", side = 1, outer = TRUE, line = 1.5, cex=0.8)
mtext("Richness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Evenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Shannon index", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.2, font=1)
mtext("Day 10", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.25, font=1)
mtext("Day 12", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.75, font=1)
```

## Correlation and Rank abundance distribution (RAD)
### This can be modified and remove
```{r, echo = FALSE, message = FALSE, include = FALSE}
#########Rarefaction######
ps.rarefied = rarefy_even_depth(otu_table(t(Table),taxa_are_rows=F), 
                                rngseed=1, sample.size=2000, replace=T)
Table_rarefied=t(ps.rarefied)
Sample_all=colnames(Table_rarefied)
Table=Table_rarefied[,which(sapply(strsplit(Sample_all, "H" , fixed = TRUE), "[", 1)=="CE1")]
Sample=colnames(Table)
```

###Data organization
```{r organize data}
##Prepare cor data
ASVreaction = data.frame(matrix(ncol = 3, nrow = nrow(Table)))
Table[apply(Table!=0, 1, all),]
for (i in 1:nrow(Table)){
  ASV=Table[i,]
  Day=sapply(strsplit(sapply(strsplit(colnames(ASV), "D" , fixed = TRUE), "[", 2), "R" , fixed = TRUE), "[", 1)
  Hratio=sapply(strsplit(sapply(strsplit(colnames(ASV), "D" , fixed = TRUE), "[", 1), "H" , fixed = TRUE), "[", 2)
  D=data.frame(t(ASV),as.numeric(Day),as.numeric(Hratio))
  colnames(D)=c("ASV","Day","Hratio")
  Day12=D[which(D$Day==12),]
  Day12[-Day12$ASV==0,]
  ASVreaction[i,1]=cor(Day12$ASV,Day12$Hratio)
  ASVreaction[i,2]=cor.test(Day12$ASV,Day12$Hratio)$p.value
  ASVreaction[i,3]=sum(Day12$ASV)
  rownames(ASVreaction)[i]=rownames(ASV)
}
colnames(ASVreaction)[3]="ReadSum"
write.csv(ASVreaction,"ASV-Hratio_atDay12.csv")
all(rownames(ASVreaction)==rownames(Table))
###Prepare relative abundance data
Day=sapply(strsplit(sapply(strsplit(colnames(Table), "D" , fixed = TRUE), "[", 2), "R" , fixed = TRUE), "[", 1)
D12_Table=Table[,which(Day==12)]
Table=Table[rowSums(Table)>0,]
Hratio=sapply(strsplit(sapply(strsplit(colnames(D12_Table), "D" , fixed = TRUE), "[", 1), "H" , fixed = TRUE), "[", 2)
SUMReadEachHratio=data.frame(
  rowSums(D12_Table[,which(Hratio==0)])/5,
  rowSums(D12_Table[,which(Hratio==5)])/5,
  rowSums(D12_Table[,which(Hratio==25)])/5,
  rowSums(D12_Table[,which(Hratio==50)])/5,
  rowSums(D12_Table[,which(Hratio==75)])/5,
  rowSums(D12_Table[,which(Hratio==100)])/5)
DATA=data.frame(ASVreaction,SUMReadEachHratio)
DATA=DATA[which(rowSums(DATA)>0),]
colnames(DATA)=c("Cor","P-value","SUM","H0Mean","H5Mean","H25Mean","H50Mean","H75Mean","H100Mean")
```


###Matching taxonomy data
```{r match/align taxonomy data}
##Let match Taxonomy!
MM=data.frame(matrix(nrow=nrow(DATA),ncol=ncol(Taxonomy)))
for (i in 1: nrow(DATA)){
  which(rownames(Taxonomy)==rownames(DATA)[i])
  MM[i,]=Taxonomy[which(rownames(Taxonomy)==rownames(DATA)[i]),1:6]
}
ALL=data.frame(DATA,MM)
colnames(ALL)[10:15]=c("Kindom","Phylum","Class","Order","Family","Genus")
ALL=ALL[which(ALL$Phylum!="<NA>"),]
ALL=ALL[which(ALL$Cor!="NA"),]
ALL$P.value[which(ALL$P.value<=0.05)]="sig"
ALL$P.value[which(as.numeric(ALL$P.value)>=0.05)]="non-sig"
COLOR=numeric()
Positive=ALL$Cor>0 & ALL$P.value=="sig"
Negative=ALL$Cor<0 & ALL$P.value=="sig"
Non=ALL$P.value=="non-sig"
COLOR[which(Positive==T)]="darkgreen"
COLOR[which(Negative==T)]="orange"
COLOR[which(Non==T)]="darkgrey"
ALL=data.frame(ALL,COLOR)

limites = c(min(ALL$SUM),
            median(ALL$SUM),
            max(ALL$SUM))
c(min(log(ALL$SUM)+0.01/1.5),
  median(log(ALL$SUM)+0.01/1.5),
  max(log(ALL$SUM)+0.01/1.5))
```

###Plot Figure4A: Correlation coefficietn
```{r plot Figure 4A}
NAME=sapply(strsplit(ALL$Order, "__" , fixed = TRUE), "[", 2)
Data=data.frame(ALL$Cor,NAME,ALL$P.value,COLOR,log(ALL$SUM)+0.01/1.5)
Data$NAME[which(is.na(Data$NAME))]="Unclassified"

P1=ggplot(data=Data,aes(y=NAME, x=ALL.Cor, horizontal=TRUE) )+
  theme_bw() + 
  geom_point(color=COLOR, 
             size = log(ALL$SUM)+0.01/1.5) +
  scale_color_manual(values = c("darkgreen","orange","darkgrey"),
                  limits = c("Incresae","Decrease","None")) +
  theme(axis.text=element_text(size=12),
        axis.title = element_text(size = 7),
        plot.margin = margin(0.05,0.05,0.001,0.05, "cm")) +
  xlab("Pearson's Correlation coefficient") +
  ylab("Order")
```

###Plote Figure 4B: Rank abundanct distribution
```{r Plot Fiugre 4B}
RADplotwithCor=function(N,i){
  ggplot(data=N, aes(x=factor(rownames(N), level = rownames(N)), y=N[,i],fill=COLOR)) +
    geom_bar(stat = "identity",width = 0.912) + 
    theme_bw() +
    theme(axis.text.x=element_blank(), 
          axis.title.x=element_blank(), 
          axis.title.y=element_blank(),  
          axis.ticks.x=element_blank()) +   ylim(0,850)+
    geom_bar(color = "black",size=0.1,stat="identity"
             ,alpha=0, position = "dodge") +
    scale_fill_manual(values = c("darkgreen","orange","darkgrey"),
                      limits = c("darkgreen","orange","darkgrey"),
                      labels = c("Increase","Decrease","None"),
                      name = "") +
    theme(axis.text=element_text(size=6),
          legend.key.size = unit(0.5, 'cm'),
          plot.margin = margin(0.05,0.05,0.001,0.05, "cm"),
          legend.text = element_text(size=7))
}

N=ALL
N=N[order(N$H0Mean,decreasing=T),]
#N=N[which(N$H0Mean>20),]
N=N[1:20,]
p1=RADplotwithCor(N,which(colnames(N)=="H0Mean"))

ALL=ALL[order(ALL$H5Mean,decreasing=T),]
N=ALL
#N=N[which(N$H5Mean>20),]
N=N[1:20,]
p2=RADplotwithCor(N,which(colnames(N)=="H5Mean"))

ALL=ALL[order(ALL$H25Mean,decreasing=T),]
N=ALL
#N=N[which(N$H25Mean>20),]
N=N[1:20,]
p3=RADplotwithCor(N,which(colnames(N)=="H25Mean"))

ALL=ALL[order(ALL$H50Mean,decreasing=T),]
N=ALL
#N=N[which(N$H50Mean>20),]
N=N[1:20,]
p12=RADplotwithCor(N,which(colnames(N)=="H50Mean"))

ALL=ALL[order(ALL$H75Mean,decreasing=T),]
N=ALL
#N=N[which(N$H75Mean>20),]
N=N[1:20,]
p5=RADplotwithCor(N,which(colnames(N)=="H75Mean"))

ALL=ALL[order(ALL$H100Mean,decreasing=T),]
N=ALL
#N=N[which(N$H100Mean>20),]
N=N[1:20,]
p6=RADplotwithCor(N,which(colnames(N)=="H100Mean"))
```

### Combine into Figure 4 
```{r plot Fiugre 4}

P2=ggarrange(p1,p2,p3,p12,p5,p6,nrow = 6,
          labels = c("0%","5%","25%","50%","75%","100%"),
          label.x=0.120, label.y=0.95, 
          font.label = list(size = 7.5),
          legend="right", common.legend = TRUE) + 
  geom_text(x=3, y=300, label="Scatter plot")

figure12=ggarrange(P1,P2,nrow=1, widths = c(1, 0.7),
                  labels = c("A","B"),
                  label.y=1.012,label.x=c(0.2,0.007),
                  font.label = list(size = 10),
                  legend="right", common.legend = TRUE) +
                  theme(plot.margin = margin(0.6,0.1,0.1,0.1, "cm"))
figure12

```

## Sumpplemenotry figures 
###Figure S1: Microbiome detachment experiment
```{r Figure S1}
#No treatment
aP1_A=46
aP2_A=134
aP3_A=139
MeanContol_T1=mean(c(aP1_A,aP2_A,aP3_A))

#rep x5
W30s1_A=91
W30s2_A=57
W30s3_A=65
T30s_x5_r1=(W30s1_A-MeanContol_T1)/MeanContol_T1
T30s_x5_r2=(W30s2_A-MeanContol_T1)/MeanContol_T1
T30s_x5_r3=(W30s3_A-MeanContol_T1)/MeanContol_T1

#rep x10
W60s1_A=69
W60s2_A=41
W60s3_A=94
T60s_x10_r1=(W60s1_A-MeanContol_T1)/MeanContol_T1
T60s_x10_r2=(W60s2_A-MeanContol_T1)/MeanContol_T1
T60s_x10_r3=(W60s3_A-MeanContol_T1)/MeanContol_T1

#rep x15
W6r1_A=40
W6r2_A=46
W6r3_A=60
T60s_x15_r1=(W6r1_A-MeanContol_T1)/MeanContol_T1
T60s_x15_r2=(W6r2_A-MeanContol_T1)/MeanContol_T1
T60s_x15_r3=(W6r3_A-MeanContol_T1)/MeanContol_T1

#######
#No treatment
bP1_A=225
bP2_A=207
bP3_A=232
bP4_A=307
MeanContol_T2=mean(c(bP1_A,bP2_A,bP3_A,bP4_A))

#rep 60sx1
W30s1_A=299
W30s2_A=257
W30s3_A=476
W30s4_A=543
W30s5_A=266
W30s6_A=160
aT60s_x1_r1=(W30s1_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r2=(W30s2_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r3=(W30s3_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r4=(W30s4_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r5=(W30s5_A-MeanContol_T2)/MeanContol_T2
aT60s_x1_r6=(W30s6_A-MeanContol_T2)/MeanContol_T2

#rep 60sx3
W60s1_A=636
W60s2_A=323
W60s3_A=337
W60s4_A=453
W60s5_A=173
W60s6_A=230
T60s_x3_r1=(W60s1_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r2=(W60s2_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r3=(W60s3_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r4=(W60s4_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r5=(W60s5_A-MeanContol_T2)/MeanContol_T2
T60s_x3_r6=(W60s6_A-MeanContol_T2)/MeanContol_T2

#rep 60sx6
W6r1_A=246
W6r2_A=269
W6r3_A=345
W6r4_A=376
W6r5_A=278
W6r6_A=181

T60s_x6_r1=(W6r1_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r2=(W6r2_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r3=(W6r3_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r4=(W6r4_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r5=(W6r5_A-MeanContol_T2)/MeanContol_T2
T60s_x6_r6=(W6r6_A-MeanContol_T2)/MeanContol_T2
#########

#No treatment
cP1_A=43
cP2_A=45
cP3_A=35
cP4_A=43
cP5_A=41
cP6_A=57
MeanContol_T3=mean(c(cP1_A,cP2_A,cP3_A,cP4_A,cP5_A,cP6_A))

#30sx1
W30s1_A=50
W30s2_A=53
W30s3_A=51
W30s4_A=51
W30s5_A=69
W30s6_A=56
T30s_x1_r1=(W30s1_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r2=(W30s2_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r3=(W30s3_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r4=(W30s4_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r5=(W30s5_A-MeanContol_T3)/MeanContol_T3
T30s_x1_r6=(W30s6_A-MeanContol_T3)/MeanContol_T3


#30sx2
W60s1_A=59
W60s2_A=73
W60s3_A=81
W60s4_A=71
W60s5_A=66
W60s6_A=63
T30s_x2_r1=(W60s1_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r2=(W60s2_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r3=(W60s3_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r4=(W60s4_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r5=(W60s5_A-MeanContol_T3)/MeanContol_T3
T30s_x2_r6=(W60s6_A-MeanContol_T3)/MeanContol_T3


# 60sx1
W6r1_A=66
W6r2_A=58
W6r3_A=60
W6r4_A=69
W6r5_A=66
W6r6_A=68
bT60s_x1_r1=(W6r1_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r2=(W6r2_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r3=(W6r3_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r4=(W6r4_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r5=(W6r5_A-MeanContol_T3)/MeanContol_T3
bT60s_x1_r6=(W6r6_A-MeanContol_T3)/MeanContol_T3

T30sx1=c(T30s_x1_r1,T30s_x1_r2,T30s_x1_r3,T30s_x1_r4,T30s_x1_r5,T30s_x1_r6)*100
T30sx2=c(T30s_x2_r1,T30s_x1_r2,T30s_x2_r3,T30s_x2_r4,T30s_x2_r5,T30s_x2_r6)*100
T30sx5=c(T30s_x5_r1,T30s_x5_r2,T30s_x5_r3)*100
T60sx1=c(bT60s_x1_r1,bT60s_x1_r2,bT60s_x1_r3,bT60s_x1_r4,bT60s_x1_r5,bT60s_x1_r6)*100
T60sx3=c(T60s_x3_r1,T60s_x3_r2,T60s_x3_r3,T60s_x3_r4,T60s_x3_r5,T60s_x3_r6)*100
T60sx6=c(T60s_x6_r1,T60s_x6_r2,T60s_x6_r3,T60s_x6_r4,T60s_x6_r5,T60s_x6_r6)*100
T60sx10=c(T60s_x10_r1,T60s_x10_r2,T60s_x10_r3)*100
T60sx15=c(T60s_x15_r1,T60s_x15_r2,T60s_x15_r3)*100

All=data.frame(T30sx1,T30sx2,T60sx1,T30sx5,T60sx3,T60sx6,T60sx10,T60sx15)

par(mar = c(5, 5, 2, 2)) # make the plots be closer together
par(mgp=c(3,1.25,0))
boxplot(All,ylab="% of living bacteria extracted with sonication",
        xlab="Sonication treatments",
        names=c("30 seconds\nx1 time","30 seconds\nx2 times","60 seconds\nx1 times",
                 "30 seconds\nx5 time","60 seconds\nx3 times","60 seconds\nx6 times",
                 "60 seconds\nx10 times","60 seconds\nx15 times"), col="white",cex.axis=0.765)
  stripchart(All, vertical = TRUE, 
           add = TRUE, pch = 20, col = 'black',cex=1.5)
abline(h=0,lty=2,col="grey")
text(2,95,paste("Mean =", format(mean(T30sx2), digits = 3)),cex=0.8)
text(3,66,paste("Mean =", format(mean(T60sx1), digits = 3)),cex=0.8)
```
###Figure S3: Additional experiment
```{r Figure S3}
###Figure2 
library(ggpubr)
library(phyloseq)
library(stats)
library(dplyr)
Table=read.table("AE_Final_table_dada2.tsv",header=T, row.names = 1)
Meta=read.csv("AE_MetaData.csv",header=T, row.names = 1)
Sample_all=colnames(Table)
ps.rarefied = rarefy_even_depth(otu_table(Table,taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T)

###############Ordination analysis##############
Table_rarefied=data.frame(t(ps.rarefied))
Sample_all=colnames(Table_rarefied)
library(vegan)
library(ape)
library(dplyr)
# First step is to calculate a distance matrix. 
# Here we use Bray-Curtis distance metric
BC_dist = avgdist(t(Table),1200,  dmethod = "bray")

# PCoA is not included in vegan. 
# We will use the ape package instead
library(ape)
# Some distance measures may result in negative eigenvalues. In that case, add a correction:
PCOA = pcoa(BC_dist, correction = "cailliez")

###Preparing my table
rownames(PCOA$vectors)==rownames(Meta)
Day=Meta$Day
Ratio=Meta$Hratio
Treatment=Meta$Treatment

MyData=data.frame(PCOA$vectors[,1],PCOA$vectors[,2],Day,Treatment,Ratio)

par(mfrow = c(2,3)) # 2-by-2 grid of plots
par(oma = c(3, 3, 1, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0), xpd=TRUE) # make the plots be closer together

DAY=c(2,4,6,8,10)
DAY_Name=c("Day 2","Day 4","Day 6","Day 8","Day 10")
Xaxis=c(F,F,T,T,T,T)
Yaxis=c(T,F,F,T,F,F)
for (i in 1:5){
  day=DAY[i]
  DDay=filter(MyData, MyData$Day==day)
  plot(DDay[,1],DDay[,2],pch=1, col="white", 
       xlim=c(min(MyData[,1]),max(MyData[,1])),
       ylim=c(min(MyData[,2]),max(MyData[,2])),
       type="b",xaxt="n",yaxt="n", 
       xlab="", ylab="")
  DD=filter(DDay, DDay$Treatment=="A")
  points(DD[,1],DD[,2],pch=1, col="black")
  
  DD=filter(DDay, DDay$Treatment=="D")
  points(DD[,1],DD[,2],pch=2, col="black")
  
  DD=filter(DDay, DDay$Treatment=="C")
  DD50=filter(DD, DD$Ratio==50)
  DD95=filter(DD, DD$Ratio==95)
  points(DD50[,1],DD50[,2],pch=17, col="grey")
  points(DD95[,1],DD95[,2],pch=17, col="black")
  
  DD=filter(DDay, DDay$Treatment=="H")
  DD50=filter(DD, DD$Ratio==50)
  DD95=filter(DD, DD$Ratio==95)
  points(DD50[,1],DD50[,2],pch=15, col="grey")
  points(DD95[,1],DD95[,2],pch=15, col="black")
  text(x=-0.325, y = 0.25, label = DAY_Name[i], cex = 1)
  DDay=filter(MyData, MyData$Day==0)
  points(DDay[,1],DDay[,2],pch=8, col="black")
  if (Xaxis[i]==T){
    axis(1, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
    axis(1, las=1, cex.axis=0.6, line = -0.55, lwd = 0)    
  }
  if (Yaxis[i]==T){
    axis(2, at = c(-0.4,-0.3,-0.2,-0.1,0,0.1, 0.2, 0.3,0.4), label = rep("", 9), tck = -0.03)
    axis(2, las=1, cex.axis=0.6, line = -0.55, lwd = 0)    
  }
}

LEGEND=c("95%-to-5% feedback-to-DOM","50%-to-50% feedback-to-DOM",
         "95%-to-5% Medium-to-DOM","50%-to-50% Medium-to-DOM",
         "100% innate DOM","C. sorokoniana",
         "Original microbiome at Day0")

legend("topleft", inset=c(1.05, 0.05),
       title = "",
       legend=LEGEND,
       pch=c(15,15,17,17,2,1,8),
       col=c("black","grey",
             "black","gray",
             "black","black","black"),
       cex=0.9, bty="n", xpd=NA)

mtext("PCoA axis 1 (38.4 %)", side = 1, outer = TRUE, line = 1.4, cex=0.8)
mtext("PCoA axis 1 (13.8 %)", side = 2, outer = TRUE, line = 1.4, cex=0.8)

```

###Figure S4: Diveristy plot 
```{r Figure S4}
#D=1, Richness
#D=2, Shannon
#D=3, Simpson
#D=4, Evenness
par(mfrow = c(3,6)) # 3-by-6 grid of plots
par(oma = c(4, 4, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together
Label=c("(a)","(b)","(c)","(d)","(e)","(f)")
Xaxis=F
Ordered_MyData=MyData[order(as.numeric(MyData$H)),]
MyData=Ordered_MyData
MyData$H=as.numeric(MyData$H)
MyData$Day=as.numeric(MyData$Day)

SplitBy_Day=split(MyData, MyData$Day)
##Plot Richness
a=5
b=41
c=5
Xaxis=FALSE
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Richness
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Richness
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}
#plot Evenness
a=0.07
b=0.5
c=0.1
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Evenness
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Evenness
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}
#plot Shannon
a=0.9
b=2.8
c=0.5
DATA=SplitBy_Day[[2]]
x=as.numeric(DATA$H)
y=DATA$Shannon
Xaxis=TRUE
DiveristyPlot_WithYaxis(x,y,a,b,c,Xaxis)
for (i in 3:7){
  DATA=SplitBy_Day[[i]]
  x=as.numeric(DATA$H)
  y=DATA$Shannon
  DiveristyPlot_NoYaxis(x,y,a,b,c,Xaxis)
}

mtext("Feedback-to-Innate index", side = 1, outer = TRUE, line = 1.5, cex=0.8)
mtext("Richness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Evenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Shannon index", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.2, font=1)
DayLab=c("Day2","Day 4","Day 6","Day 8","Day 10","Day 12")
mtext(DayLab, side = 3, outer = TRUE, line = 0, cex=0.8, 
      at=c(0.075,0.25,0.425,0.575,0.75,0.925), font=1)



```



###Figure S5 and S6: Richness and eveness in function of select phyla 
```{r Figure S5 and S6}

Table_oldold=read.table("Final_table_dada2.tsv",header=T, row.names = 1)
Meta=read.csv("MetaData.csv",header=T, row.names = 1)
Taxonomy=read.csv("metadata_taxonomy_HandMade.csv",header=T, row.names = 1)

###remove Bacteria-unclassified####
Table_Alpha=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Alphaproteobacteria"),]),]
Table_Bact=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Bacteroidia"),]),]
Table_Gamma=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Gammaproteobacteria"),]),]
GammaTax=which(Taxonomy$D2=="D_2__Gammaproteobacteria")

Table_Actino=Table_oldold[row.names(Table_oldold) %in% rownames(Taxonomy[which(Taxonomy$D2=="D_2__Actinobacteria"),]),]


FigureS4_Diveristy=function(Table_old){
  #########Rarefaction######
  ps.rarefied = rarefy_even_depth(otu_table(t(Table_old),taxa_are_rows=F), rngseed=1, sample.size=2000, replace=T)
  
  Table_rarefied=t(ps.rarefied)
  Sample_all=colnames(Table_rarefied)
  Table=Table_rarefied[,which(sapply(strsplit(Sample_all, "H" , fixed = TRUE), "[", 1)=="CE1")]
  ##########################
  
  Richness=colSums(ifelse(Table> 1,1,0))
  Shannon=diversity(t(Table),"shannon")
  Simpson=diversity(t(Table),"simpson")
  invSimpson=diversity(t(Table),"invsimpson")
  Evenness=invSimpson/Richness
  Day=sapply(strsplit(sapply(strsplit(names(Richness), "D" , fixed = TRUE), "[", 2),"R",fixed=T),"[",1)
  H=sapply(strsplit(sapply(strsplit(names(Richness), "H" , fixed = TRUE), "[", 2),"D",fixed=T),"[",1)
  MyData=data.frame(Richness,Shannon,Simpson,Evenness,Day,H)
  return(MyData)
  ##########################
}
Alpha=FigureS4_Diveristy(Table_Alpha)
Gamma=FigureS4_Diveristy(Table_Gamma)
Bact=FigureS4_Diveristy(Table_Bact)
#Beta=FigureS4_Diveristy(Table_Beta)

Diveristy_Day8_10_12=function(MyData){
  Ordered_MyData=MyData[order(as.numeric(MyData$H)),]
  MyData=Ordered_MyData
  MyData$H=as.numeric(MyData$H)
  
  DDay8=filter(MyData, MyData$Day==8)
  DDay10=filter(MyData, MyData$Day==10)
  DDay12=filter(MyData, MyData$Day==12)
  LIST=list(DDay8,DDay10,DDay12)
  return(LIST)
}

Alpha_list=Diveristy_Day8_10_12(Alpha)
Gamma_list=Diveristy_Day8_10_12(Gamma)
Bact_list=Diveristy_Day8_10_12(Bact)

#####Diversity plot###
source("Functions_20220504.R")
par(mfrow = c(3,2)) # 3-by-6 grid of plots
par(oma = c(4, 5.5, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together


Each_plot=function(DDay10,D,Xaxis,Yaxis,a,b,c){
  
  plot(as.numeric(DDay10$H),DDay10[,D], xaxt="n", yaxt="n",
       ylim=c(a,b),
       xlim=c(-5,105))
  
  # fit the 2rd quadrilles regressions
  y=DDay10[,D]
  x=DDay10$H
  fit2 <- lm(y~poly(x,2,raw=TRUE))
  xx <- seq(0,100, length=50)
  summary(fit2)
  p2=summary(fit2)$coefficient[3,4]
  if (p2<=0.05){L2=1}else{L2=2}
  if (p2<=0.001){p2="<0.001"}else{p2=p2}
  lines(xx, predict(fit2, data.frame(x=xx)), col="blue",lty=L2)
  
  # fit the linear regression
  l=lm(DDay10[,D]~as.numeric(DDay10$H))
  p=summary(l)$coefficient[2,4]
  if (p<=0.05){L=1}else{L=2}
  if (p<=0.001){p="<0.001"}else{p=p}
  abline(l,lty=L)
  State = vector('expression',2)
  State[1] = substitute(expression(italic(p1:p-value) == MYVALUE), 
                        list(MYVALUE = format(p, digits = 2)))[2]
  State[2] = substitute(expression(italic(p2:p-value) == MYVALUE), 
                        list(MYVALUE = format(p2, digits = 2)))[2]
  
  legend("topright",legend=State, bty = 'n',cex=0.8,text.col=c("black","blue"))
  #text(-4.5,b*0.99, label = Label1, cex=0.9)
  
  if (Xaxis==TRUE) {
    axis(1, at = c(0,25,50,75,100), 
         label = rep("", 5), 
         tck = -0.04)
    axis(1, at = c(0,25,50,75,100), 
         label = c("0%","25%","50%","75%","100%"), 
         cex.axis=0.6,line = -0.7, lwd = 0)
    axis(1, at = 5, 
         label = "", 
         tck = -0.03)
    axis(1, at = 5, 
         label = "5%", 
         cex.axis=0.6,line = -1.1, lwd = 0)
  }
  
  if (Yaxis==TRUE) {
    axis(2, tck = -0.04, at = seq(a,b, by = c), 
         label = rep("", length(seq(a,b, by = c))))
    axis(2, las=1, cex.axis=0.7, at = seq(a,b, by = c),
         line = -0.4, lwd = 0)
  }
  
  
}  

Each_plot(Alpha_list[[2]],1,FALSE,TRUE,1,15,2)
Each_plot(Alpha_list[[3]],1,FALSE,FALSE,1,15,2)

Each_plot(Gamma_list[[2]],1,FALSE,TRUE,1,15,2)
Each_plot(Gamma_list[[3]],1,FALSE,FALSE,1,15,2)


Each_plot(Bact_list[[2]],1,TRUE,TRUE,1,15,2)
Each_plot(Bact_list[[3]],1,TRUE,FALSE,1,15,2)


mtext("Feedback-to-innate index", side = 1, outer = TRUE, line = 2, cex=0.8)
mtext("Alphaproteobacteria\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Gammaproteobacteria\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Bacteroidia\nrichness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.15,font=1)
mtext("Day 10", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.25, font=1)
mtext("Day 12", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.75, font=1)

######Evenness #######
#####Diversity plot###
source("Functions_20220504.R")
par(mfrow = c(3,2)) # 3-by-6 grid of plots
par(oma = c(4, 5.5, 2, 1)) # make room for the overall x and y axis titles
par(mar = c(0, 0, 0, 0)) # make the plots be closer together

Each_plot(Alpha_list[[2]],4,FALSE,TRUE,0,0.7,0.2)
Each_plot(Alpha_list[[3]],4,FALSE,FALSE,0,0.7,0.2)

Each_plot(Gamma_list[[2]],4,FALSE,TRUE,0,0.7,0.2)
Each_plot(Gamma_list[[3]],4,FALSE,FALSE,0,0.7,0.2)

Each_plot(Bact_list[[2]],4,TRUE,TRUE,0,0.7,0.2)
Each_plot(Bact_list[[3]],4,TRUE,FALSE,0,0.7,0.2)

mtext("Feedback-to-innate index", side = 1, outer = TRUE, line = 2, cex=0.8)
mtext("Alphaproteobacteria\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.85, font=1)
mtext("Gammaproteobacteria\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.5,font=1)
mtext("Bacteroidia\nevenness", side = 2, outer = TRUE, line = 2, cex=0.8, at=0.15,font=1)
mtext("Day 10", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.25, font=1)
mtext("Day 12", side = 3, outer = TRUE, line = 0, cex=0.8, at=0.75, font=1)
```
